The value of intermediation

### 2022-09-15 src/presentation/presentation.qmd
Fix Shapley-value example
Speed up main proposition figure

 - A wholesale producer: $P$
 - Two downstream resellers: $A_1, A_2$

@@

::: {.column .fragment width="40%"}
And the following achievable profits:

Coalition | Profits
----------|---------
$\{P\},  \{A_i\}$     |  0
$\{A_1, A_2\}$  | 0  
$\{P, A_i\}$  | 2 
$\{P, A_1, A_2\}$  | 3
:::

@@

::: {.column width="40%"}
And the following achievable profits:

Coalition | Profits
----------|---------
$\{P\},  \{A_i\}$     |  0
$\{A_1, A_2\}$  | 0
$\{P, A_i\}$  | 2 
$\{P, A_1, A_2\}$  | 3
:::

@@

::: {.fragment .fade-in fragment-index=2}
Shapley value:
$$
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
:::
::: {.fragment .fade-in fragment-index=4}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

::: {.fragment fragment-index=1}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
:::
::: {.fragment fragment-index=2}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/add_brace.mp4" />
:::
::: {.fragment fragment-index=3}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/more_firms.mp4" />
:::
::: {.fragment fragment-index=4}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/continuous_approximation.mp4" />
:::
::: {.fragment fragment-index=5}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />
:::

>>>>

 - Two producers: $A_1, A_2$
   - can each make \$1 on their own
 - A platform: $P$
   - Triples the firms' profits

@@

::: {.column .fragment width="40%"}
Coalition | Profits
----------|---------
$\{P\}$     |  0
$\{A_i\}$   | 1
$\{A_1, A_2\}$  | 2
$\{P, A_i\}$  | 3
$\{P, A_1, A_2\}$  | 6
:::

@@

::: {.column width="40%"}
Coalition | Profits
----------|---------
$\{P\}$     |  0
$\{A_i\}$   | 1
$\{A_1, A_2\}$  | 2
$\{P, A_i\}$  | 3
$\{P, A_1, A_2\}$  | 6
:::

@@

::: {.fragment .fade-in fragment-index=2}
Shapley value:
$$
\scriptsize
\varphi_P^n(f) = \frac{1}{n+1} \sum_{k=0}^{n} f(k)
$$
:::
::: {.fragment .fade-in fragment-index=5}
$$
\scriptsize
\to \int_0^1 f(t) \, \mathrm{d}t
$$
:::

@@

::: {.fragment fragment-index=1}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/draw_bars.mp4" />
:::
::: {.fragment fragment-index=2}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/add_brace.mp4" />
:::
::: {.fragment fragment-index=3}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/more_firms.mp4" />
:::
::: {.fragment fragment-index=4}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/continuous_approximation.mp4" />
:::
::: {.fragment fragment-index=6}
   <video data-autoplay src="../../out/manim_figures/videos/proposition_main/800p60/sections/surplus_division.mp4" />
:::
